10th International Satisfiability Modulo Theories Competition (SMT-COMP 2015): Rules and Procedures

### 2015-05-31 rules/rules15.tex
Postprocessor: name fixed.
David's email address updated.

\author{%
Sylvain Conchon \\
Paris-Sud University \\
France \\
{\small\href{mailto:Sylvain.Conchon@lri.fr}{\tt Sylvain.Conchon@lri.fr}} \\
\and
David D{\'e}harbe \\
Federal University of Rio Grande do Norte \\
Brazil \\
{\small\href{mailto:David.Deharbe@loria.fr}{\tt David.Deharbe@loria.fr}} \\
\and
Tjark Weber \\
Uppsala University \\
Sweden \\
{\small\href{mailto:tjark.weber@it.uu.se}{\tt tjark.weber@it.uu.se}} \\
\\
}

@@

The main track competition uses a StarExec post-processor (named
``SMT-COMP 2015 Main Track Postprocessor") to accumulate the results.

>>>>

\author{%
Sylvain Conchon \\
Paris-Sud University \\
France \\
{\small\href{mailto:Sylvain.Conchon@lri.fr}{\tt Sylvain.Conchon@lri.fr}} \\
\and
David D{\'e}harbe \\
Federal University of Rio Grande do Norte \\
Brazil \\
{\small\href{mailto:david@dimap.ufrn.br}{\tt david@dimap.ufrn.br}} \\
\and
Tjark Weber \\
Uppsala University \\
Sweden \\
{\small\href{mailto:tjark.weber@it.uu.se}{\tt tjark.weber@it.uu.se}} \\
\\
}

@@

The main track competition uses a StarExec post-processor (named
``SMTCOMP2015") to accumulate the results.
